---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qplots
## Overview

<!-- badges: start -->
<!-- badges: end -->

qplots provides a function to plot the distribution of variables in a data frame so that basic statistics of variables can be obtained immediately.

* `diquick_dist()`: Plots density distribution of numeric variables and bar plot of category/factor variables in a data frame.
  
## Installation

You can install the development version of qplots from the GitHub repository like so:

``` r
devtools::install_github("HosseinEbrahimiK/qplots")
```

## Usage

These are basic examples that demonstrate some use cases of our function for datasets. We have used the `gapminder` dataset for this purpose. The first two examples are numerical variables, and the outputs are density distributions as expected. The last example includes a categorical column in the data, which the result will be a bar plot of frequencies.

```{r example}
library(qplots)

quick_dist(gapminder::gapminder, "lifeExp") # a numeric variable
quick_dist(gapminder::gapminder, "gdpPercap") # a numeric variable
quick_dist(gapminder::gapminder, "continent") # a categorical variable

```

## Getting help

If you encounter a clear bug, please file an issue with a minimal
reproducible example on
[GitHub](https://github.com/HosseinEbrahimiK/qplots/issues).

-----

Please note that this package is a part of assignments of *[STAT 545B @ UBC](https://stat545.stat.ubc.ca/syllabus-545b/)* course.
