---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qplots

<!-- badges: start -->
<!-- badges: end -->

The goal of qplots is to quickly plot variables of a data frame so that you can obtain basic information regarding variables of the data.

## Installation

You can install the development version of qplots from the GitHub repository like so:

``` r
devtools::install_github("HosseinEbrahimiK/qplots")
```

## Example

This is a basic example which shows you how to solve a common problem within a dataframe. Here, we have used `gapminder` dataset as an example:

```{r example}
library(qplots)

quick_dist(gapminder::gapminder, "lifeExp") # a numeric variable
quick_dist(gapminder::gapminder, "gdpPercap") # a numeric variable
quick_dist(gapminder::gapminder, "continent") # a categorical variable

```
